Service Chain Placement in SDNs\tnoteref{t1}

### 2019-03-13 src/chain.tex
amiri

Foerster, Parham and Schmid~\cite{FPS17} considered the
\textsc{Bidirectional Waypoint Routing} problem, where the input
consists of a graph $G = (V,E)$ with edge weights and capacities, a
source $s$, a destination $t$, and a subset of the vertices $W$.  A
feasible solution is a route from $s$ to $t$ that visits the vertices
in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
according to the given order.  The goal is to find a minimum weight
solution.
%
Foerster et al.~\cite{FPS17} showed that the unordered
problem has no PTAS, assuming P$\neq$NP and gave a
$1.53$-approximation algorithm.  They also presented polynomial time
algorithms for special cases.
%
As for the ordered variant, they showed that feasible routes can be
computed efficiently if $\abs{W} = O(1)$.  In addition, they showed
that the problem is NP-hard and gave a polynomial time algorithm for
cactus graphs with constant link capacities.

>>>>

\fix{Amiri1 et al.~\cite{AmiriLatin2018, AmiriCCR2018, AmiriIFIP2018} considered the \textsc{Waypoint Routing} problem.
In this problem we are given an edge weighted graph $G=(V, E)$, a source $s \in V$, destination $t \in V$ and a set of waypoints $W \subseteq V$.
The goal is to find a shortest walk from $s$ to $t$ that traverses all the waypoints.
Two variants of this problem exists, namely when the waypoints need to be traversed in a particular or in an arbitrary order.
It is also possible that we have additional capacity consistents, i.e. a limitation on the number of times a walk can go through each edge.
Amiri1 et al. show that (i) There exists a polynomial algorithm for bounded treewidth graph for arbitrary number of waypoints and for general graphs for logarithmically bounded number of waypoints. (ii) This problem is NP-hard in general. (iii) This problem is NP-hard for directed graphs even when there is a single waypoint. (iv) There is a polynomial algorithm for cactus topologies.
}

% Foerster, Parham and Schmid~\cite{FPS17} considered the
% \textsc{Bidirectional Waypoint Routing} problem, where the input
% consists of a graph $G = (V,E)$ with edge weights and capacities, a
% source $s$, a destination $t$, and a subset of the vertices $W$.  A
% feasible solution is a route from $s$ to $t$ that visits the vertices
% in $W$.  If $W$ is ordered, the route should visit the vertices of $W$
% according to the given order.  The goal is to find a minimum weight
% solution.
% %
% Foerster et al.~\cite{FPS17} showed that the unordered
% problem has no PTAS, assuming P$\neq$NP and gave a
% $1.53$-approximation algorithm.  They also presented polynomial time
% algorithms for special cases.
%
As for the ordered variant, they showed that feasible routes can be
computed efficiently if $\abs{W} = O(1)$.  In addition, they showed
that the problem is NP-hard and gave a polynomial time algorithm for
cactus graphs with constant link capacities.
